### 2015-06-09 text/ms.Rmd
Quick copy editing of ms; mostly spelling

Here, we develop ensemble models to estimate the population status of exploited
fish populations. We explore a variety of ensemble approaches applied to both
simulated and real-world fish stocks and compare predictive performance. In
developing these models we highlight the types of problems one encounters when
forming and evaluating ensemble models. We find that ensembles generally
provide improved predictive performance than any single model---especially when
considered across multiple dimensions of predictive ability. Furthermore, the
output from ensemble models can provide better mechanistic understanding of how
invidual models perform.

@@

We first developed and tested ensemble models with a fully factorial simulated
dataset [@rosenberg2014]. The simulation models included three life histories (small
pelagic, demersal, large pelagic), three levels of how depleted biomass was at
the start of the dataset (100%, 70%, and 40% of carrying capacity), four
harvest dynamics (a constant harvest rate, a harvest rate that is coupled with
biomass to mimic an open-access single-species fishery, a scenario where
harvest rate increases to a fixed level, a 'roller-coaster' scenario where the
harvest rate increases, maintains a steady level and decreases to a lower
steady level). Process noise was introduced to the models through two levels of
multiplicative recruitment variability ($N(0, 0.2)$ and $N(0, 0.6)$, two levels
of first-order autoregressive correlation on recruitment variablity (0 and
0.6). The simulation included a scenario without observation error and with
multiplicative observation error around catch at $N(0, 0.2)$.

@@

A critical component to any predictive modelling exercise is to evaluate the
performance of a model new data [@hastie2009]. We used repeated three-fold
cross validation to test predictive performance: we randomly divided the
dataset into three sets, built ensemble models on two-thirds of the data, and
evaluated predictive performance on the remaining third of the data. We
repeated this across each of the three splits and then repeated the whole
procedure XX times to account for bias that may result from any one set of
validation splits. Since the dynamics of simulated populations differing only
in the magnitude of observation error around catch, magnitude of recuitment
variability, or stochastic draw of these values are likely similar, we grouped
these characteristics together in the cross-validation process---we never
trained and tested on models differing only in these characteristics.

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, peformance metrics often measure some form of bias,
precision, accuracy (a combination of bias and precision), or the ability to
correctly rank or correlate across populations. Here, we measure proportional
error (PE; also called 'relative error') defined as $(\hat{b} - b)/b$. We
summarize median proportional error to measure bias, median absolute
proportional error to measure accuracy, and Spearman's rank-order correlation
to measure the ability to correctly rank populations.

>>>>

Here, we develop ensemble models to estimate the population status of exploited
fish populations. We explore a variety of ensemble approaches applied to both
simulated and real-world fish stocks and compare predictive performance. In
developing these models we highlight the types of problems one encounters when
forming and evaluating ensemble models. We find that ensembles generally
provide improved predictive performance than any single model---especially when
considered across multiple dimensions of predictive ability. Furthermore, the
output from ensemble models can provide better mechanistic understanding of how
individual models perform.

@@

We first developed and tested ensemble models with a fully factorial simulated
dataset [@rosenberg2014]. The simulation models included three life histories: small
pelagic, demersal, large pelagic; three levels of how depleted biomass was at
the start of the dataset: 100%, 70%, and 40% of carrying capacity; and four
harvest dynamics: a constant harvest rate, a harvest rate that is coupled with
biomass to mimic an open-access single-species fishery, a scenario where
harvest rate increases to a fixed level, a 'roller-coaster' scenario where the
harvest rate increases, maintains a steady level and decreases to a lower
steady level. Process noise was introduced to the models through two levels of
multiplicative recruitment variability: $N(0, 0.2)$ and $N(0, 0.6)$, two levels
of first-order autoregressive correlation on recruitment variability: 0 and
0.6. The simulation included a scenario without observation error and with
multiplicative observation error around catch at $N(0, 0.2)$.

@@

A critical component to any predictive modelling exercise is to evaluate the
performance of a model new data [@hastie2009]. We used repeated three-fold
cross validation to test predictive performance: we randomly divided the
dataset into three sets, built ensemble models on two-thirds of the data, and
evaluated predictive performance on the remaining third of the data. We
repeated this across each of the three splits and then repeated the whole
procedure XX times to account for bias that may result from any one set of
validation splits. Since the dynamics of simulated populations differing only
in the magnitude of observation error around catch, magnitude of recruitment
variability, or stochastic draw of these values are likely similar, we grouped
these characteristics together in the cross-validation process---we never
trained and tested on models differing only in these characteristics.

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of bias,
precision, accuracy (a combination of bias and precision), or the ability to
correctly rank or correlate across populations. Here, we measure proportional
error (PE; also called 'relative error') defined as $(\hat{b} - b)/b$. We
summarize median proportional error to measure bias, median absolute
proportional error to measure accuracy, and Spearman's rank-order correlation
to measure the ability to correctly rank populations.
